Real-Time Certified Probabilistic Pedestrian Forecasting

### 2017-02-16 pedestrian_forecasting_iros_2017.tex
reformulated the disccussion after theorem 3

To begin, rather than focusing on computing $\rho_t(x_t)$, we describe how to compute the joint probability $\Pr( x_t , \hat{x}_0, \hat{v}_0)$.
We can obtain $\rho_t(x_t)$ by normalizing $\Pr( x_t , \hat{x}_0, \hat{v}_0)$ with respect to integration over $x_t$.
We can approximate the integration over $s$ in \eqref{eq:decomposition}, with a Riemann sum.
Given a regular partition $\{ s_0, s_1, \dots, s_n \}$ of step-size $\Delta s > 0$ on the support of $\Pr(s)$, 
we can conclude that the integral term in \eqref{eq:decomposition} can be approximated by
\begin{align}
	\begin{split}
	&\sum_{k} \int \Pr( x_t, k , s , \hat{x}_0, \hat{v}_0 ) ds = \\
	 &\underbrace{\Delta s \sum_{j} \sum_{k} \Pr( x_t, k , s_j , \hat{x}_0, \hat{v}_0)}_{\text{approximation}}
	  +
	  \underbrace{\varepsilon_s}_{\text{error}}
	 \end{split} \label{eq:approximation 0}
\end{align}
where the error is bounded by $\int| \varepsilon_s | ds \leq  TV(x_t, \hat{x}_0, \hat{v}_0) \Delta s$
where $TV(x_t, \hat{x}_0, \hat{v}_0)$ is the sum, with respect to $k$, of the total variation of $\Pr( x_t, k , s, \hat{x}_0, \hat{v}_0 )$ with respect to $s$ for fixed $x_t, \hat{x}_0, \hat{v}_0$.
Since this error term can be controlled, the problem of solving $\rho_t(x_t)$ is reduced to that of efficiently computing $ \Pr( x_t, k , s_j, \hat{x}_0, \hat{v}_0)$
for a fixed collection of $s_j$'s.

@@

Corollary \ref{cor:error} justifies using \eqref{eq:approximation 2} as an approximation of $\Pr( x_t, k,s,\hat{x}_0, \hat{v}_0)$.
In particular, this reduces the problem of computing $\rho_t(x_t)$ to the problem of computing the weights $W(k,s,i,j,\hat{x}_0)$ and the points $\Phi_{k,s}^t(x_0^{i,j})$ for all $k,s$ and points $x_0^{i,j} \in \Gamma_L( \hat{x}_0; N_x)$.
We can reduce this burden further by exploiting the following symmetry:
\begin{thm} \label{thm:symmetry}
	$\Phi_{k,s}^t = \Phi_{k,1}^{st}$.
\end{thm}
\begin{proof}
	Say $x(t)$ satisfies the ordinary differential equation $x'(t) = sX_k(x(t))$ with the initial condition $x_0$.
	In other words, $x(t) = \Phi_{k,s}^{t}(x_0)$.
	Taking a derivative of $x(t/s)$, we see $\frac{d}{dt} (x(t/s)) = x'(t/s) /s = X_k(x(st))$.
	Therefore $x(t/s) = \Phi_{k,1}^{t}( x_0)$.
	Substitution of $t$ with $\tau = t/s$ yields $x(\tau) = \Phi_{k,1}^{s \tau} (x_0)$.
	As $x(\tau) = \Phi_{k,s}^{\tau}(x_0)$ as well, the result follows.
\end{proof}
This, allows us to compute $\Phi_{k,s}^t( x_0^{\alpha})$ using computations of $\Phi_{k,1}^t(x_0^{\alpha})$, which yields the following result:
\begin{thm} \label{thm:main}
	Let $\{s_1,\dots,s_n\}$ be a regular partition on the support of $\Pr(s)$.
	Then the density
	\begin{align}
		\begin{split}
		&\Delta s \sum_{i,j,k,\ell} W(k,s_\ell,i,j,\hat{x}_0) \left. \Pr( x_t \mid \check{x}_t ) \right|_{ \check{x}_t = \Phi_{k,1}^{s_\ell t}( x_0^{i,j}) } \\
		&+\Pr( x_t , lin, \hat{x}_0, \hat{v}_0 )
		\end{split}
		\label{eq:approximation 3}
	\end{align}
	approximates $\Pr( x_t, \hat{x}_0, \hat{v}_0)$ with an error of size $\mathcal{O}( \Delta s + \Delta x + \varepsilon_{\rm tol})$.
\end{thm}
\begin{proof}
	Substitute Theorem \ref{thm:symmetry} into Corollary \ref{cor:error}, to replace $\Phi_{k,s}^t$ with $\Phi_{k,1}^{st}$.
	This gives us an error term of size $\Delta x$, if we compute the integral over $s$ exactly.
	Using \eqref{eq:approximation 0}, we can compute the integral over $s$ approximately, with an error of magnitude $\Delta s$.
\end{proof}

This is a powerful result, since if $\Pr(s)$ has a support contained within the domain $[-\bar{s}, \bar{s}]$, then to solve for $\Pr( x_t, \hat{x}_0, \hat{v}_0)$  (and thus $\rho_t(x_t)$) at times $0, \Delta t, \dots, N_t \Delta t$, we only need to compute $\Phi_{k,1}^{\ell \Delta t \bar{s}}$ for each $\ell \in  \{-N_t,\dots,N_t\}$ once.
This is because, once $\Phi_{k,1}^{\ell \Delta t \bar{s}}$ is computed for each $\ell \in \{-N_t, \dots ,N_t\}$ we can use the partition of $[-\bar{s}, \bar{s}]$ given by $\{ \bar{s} \frac{m}{\ell} \}_{m=-\ell}^{\ell}$ to compute a $\Delta s = \bar{s} / \ell$ accurate approximation for each $\ell$, courtesy of Theorem \ref{thm:main}.
%Admittedly, this means our approximations might be imprecise over very short times, but more accurate over longer time-horizons.
The procedure to compute  $\rho_t(x_t)$ is summarized in Algorithm \ref{alg:1}.

\begin{algorithm}[t]
		  \caption{Algorithm to Compute  $\rho_t$.}
		  \label{alg:1}
		  \begin{algorithmic}[1]
		    \Require $N_t \in \mathbb{N},  \{ X_k \}_{k=1}^{n}, \hat{x}_0, \hat{v}_0, \Gamma_L( \hat{x}_0, N_x)$, and the posteriors of \eqref{eq:pgm}.
		    \ForEach {$m \in \{ -\ell,\dots,\ell \}$}
		    \State Compute $W(k,s,i,j,\hat{x}_0)$ for $s = \bar{s} m / \ell$.
		    \EndFor  
		    \State Construct a $\mathcal{O}( \Delta x + \bar{s}/\ell + \varepsilon_{\rm tol})$ approximation of $\Pr(\check{x}_t, \hat{x}_0, \hat{v}_0)$ at $t=\ell \Delta t$ via Theorem \ref{thm:main} \label{alg1:step2}.
		    \State Normalize with respect to $\check{x}_t$ to obtain an approximation of $\Pr(\check{x}_t \mid \hat{x}_0, \hat{v}_0)$.
		    \State Convolve with respect to $\Pr( x_t \mid \check{x}_t)$ to obtain $\rho_t(x_t)$ at $t= \ell \cdot \Delta t$
		  \end{algorithmic}
\end{algorithm}

>>>>

To begin, rather than focusing on computing $\rho_t(x_t)$, we describe how to compute the joint probability $\Pr( x_t , \hat{x}_0, \hat{v}_0)$.
We can obtain $\rho_t(x_t)$ by normalizing $\Pr( x_t , \hat{x}_0, \hat{v}_0)$ with respect to integration over $x_t$.
We can approximate the integration over $s$ in \eqref{eq:decomposition}, with a Riemann sum.
Let us assume that $\Pr(s \mid k)$ is compactly supported for all $k = 1,\dots,n$, and the supported is always contained
in some interval $[ - \bar{s} , \bar{s} ]$ for some $\bar{s} > 0$.
Given a regular partition $\{ s_0, s_1, \dots, s_n \}$ of step-size $\Delta s > 0$ on $[-\bar{s}, \bar{s}]$, 
we can conclude that the integral term in \eqref{eq:decomposition} can be approximated by
\begin{align}
	\begin{split}
	&\sum_{k} \int \Pr( x_t, k , s , \hat{x}_0, \hat{v}_0 ) ds = \\
	 &\underbrace{\Delta s \sum_{j} \sum_{k} \Pr( x_t, k , s_j , \hat{x}_0, \hat{v}_0)}_{\text{approximation}}
	  +
	  \underbrace{\varepsilon_s}_{\text{error}}
	 \end{split} \label{eq:approximation 0}
\end{align}
where the error is bounded by $\int| \varepsilon_s | ds \leq  TV(x_t, \hat{x}_0, \hat{v}_0) \Delta s$
where $TV(x_t, \hat{x}_0, \hat{v}_0)$ is the sum, with respect to $k$, of the total variation of $\Pr( x_t, k , s, \hat{x}_0, \hat{v}_0 )$ with respect to $s$ for fixed $x_t, \hat{x}_0, \hat{v}_0$.
Since this error term can be controlled, the problem of solving $\rho_t(x_t)$ is reduced to that of efficiently computing $ \Pr( x_t, k , s_j, \hat{x}_0, \hat{v}_0)$
for a fixed collection of $s_j$'s.

@@

Corollary \ref{cor:error} justifies using \eqref{eq:approximation 2} as an approximation of $\Pr( x_t, k,s,\hat{x}_0, \hat{v}_0)$.
In particular, this reduces the problem of computing $\rho_t(x_t)$ to the problem of computing the weights $W(k,s,i,j,\hat{x}_0)$ and the points $\Phi_{k,s}^t(x_0^{i,j})$ for all $k,s$ and points $x_0^{i,j} \in \Gamma_L( \hat{x}_0; N_x)$.
We can reduce this burden further by exploiting the following symmetry:
\begin{thm} \label{thm:symmetry}
	$\Phi_{k,s}^t = \Phi_{k,1}^{st}$.
\end{thm}
\begin{proof}
	Say $x(t)$ satisfies the ordinary differential equation $x'(t) = sX_k(x(t))$ with the initial condition $x_0$.
	In other words, $x(t) = \Phi_{k,s}^{t}(x_0)$.
	Taking a derivative of $x(t/s)$, we see $\frac{d}{dt} (x(t/s)) = x'(t/s) /s = X_k(x(st))$.
	Therefore $x(t/s) = \Phi_{k,1}^{t}( x_0)$.
	Substitution of $t$ with $\tau = t/s$ yields $x(\tau) = \Phi_{k,1}^{s \tau} (x_0)$.
	As $x(\tau) = \Phi_{k,s}^{\tau}(x_0)$ as well, the result follows.
\end{proof}
This, allows us to compute $\Phi_{k,s}^t( x_0^{\alpha})$ using computations of $\Phi_{k,1}^t(x_0^{\alpha})$, which yields the following result:
\begin{thm} \label{thm:main}
	Let $\{s_1,\dots,s_n\}$ be a regular partition on the support of $\Pr(s)$.
	Then the density
	\begin{align}
		\begin{split}
		&\Delta s \sum_{i,j,k,m} W(k,s_m,i,j,\hat{x}_0) \left. \Pr( x_t \mid \check{x}_t ) \right|_{ \check{x}_t = \Phi_{k,1}^{s_m t}( x_0^{i,j}) } \\
		&+\Pr( x_t , lin, \hat{x}_0, \hat{v}_0 )
		\end{split}
		\label{eq:approximation 3}
	\end{align}
	approximates $\Pr( x_t, \hat{x}_0, \hat{v}_0)$ with an error of size $\mathcal{O}( \Delta s + \Delta x + \varepsilon_{\rm tol})$.
\end{thm}
\begin{proof}
	Substitute Theorem \ref{thm:symmetry} into Corollary \ref{cor:error}, to replace $\Phi_{k,s}^t$ with $\Phi_{k,1}^{st}$.
	This gives us an error term of size $\Delta x$, if we compute the integral over $s$ exactly.
	Using \eqref{eq:approximation 0}, we can compute the integral over $s$ approximately, with an error of magnitude $\Delta s$.
\end{proof}

This is a powerful result, because it allows us to solve for $\Pr( x_t, \hat{x}_0, \hat{v}_0)$  (and thus $\rho_t(x_t)$) at times $t=\Delta t, \dots, N_t \Delta t$ by a single computation of $\Phi_{k,1}^{\ell \Delta t \bar{s}}( x_0^{i,j})$ for each $\ell \in  \{-N_t,\dots,N_t\}$, $k \in \{1,\dots,n\}$, and $x_0^{i,j} \in \Gamma_L( \hat{x}_0 , N_x)$.
To explain this, assume we are given $\Phi_{k,1}^{m \Delta t \bar{s}}(x_0^{i,j})$ for all $|m| \leq \ell$.
We can then use the regular partition
\begin{align}
	\mathcal{P}_\ell := \left\{ \frac{m}{\ell} \bar{s} \right\}_{m=-\ell}^{\ell} \label{eq:partition}
\end{align}
of $[-\bar{s}, \bar{s}]$ to compute a Riemann sum approximation using Theorem \ref{thm:main}.
The partition $\mathcal{P}_\ell$ has a width of size, $\Delta s = \bar{s} / \ell$, and substitution in \eqref{eq:approximation 3} yields an approximation of $\Pr( x_t, \hat{x}_0, \hat{v}_0)$ given by
\begin{align*}
	\begin{split}
		&\frac{\bar{s}}{\ell} \sum_{i,j,k,m} W(k,m \bar{s} / \ell ,i,j,\hat{x}_0) \left. \Pr( x_t \mid \check{x}_t ) \right|_{ \check{x}_t = \Phi_{k,1}^{m \bar{s} \Delta t}( x_0^{i,j}) } \\
		&\qquad+\Pr( x_t , lin, \hat{x}_0, \hat{v}_0 ).
	\end{split}
\end{align*}
As we've already computed $\Phi_{k,1}^{m \bar{s} \Delta t}$ for $| m | \leq \ell$ by assumption, the only obstacle to computing this sum is the computation of the weights $W(k,m \bar{s} / \ell ,i,j,\hat{x}_0)$.
%Admittedly, this means our approximations might be imprecise over very short times, but more accurate over longer time-horizons.
The procedure to compute  $\rho_t(x_t)$ is summarized in Algorithm \ref{alg:1}.

\begin{algorithm}[t]
		  \caption{Algorithm to Compute  $\rho_t$ at times $t= \Delta t, 2 \Delta t, \dots, N_t \Delta t$.}
		  \label{alg:1}
		  \begin{algorithmic}[1]
		    \Require $\bar{s} > 0, N_t \in \mathbb{N}, \Delta t > 0,   \{ X_k \}_{k=1}^{n}, \hat{x}_0, \hat{v}_0, \Gamma_L( \hat{x}_0, N_x)$,
		    routines for $\Pr(x_0 \mid M), \Pr(x_0 \mid \hat{x}_0), \Pr(v_0 \mid \hat{v}_0 ), \Pr(M \in \mathcal{M}), \Pr(s \mid k)$ .
		    \For {$\ell = 1,\dots,N_t$}
		    \State Compute and store $\Phi_{k,1}^{ \pm \bar{s} \ell \Delta t}( x_0^{i,j} )$ for all $x_0^{i,j} \in \Gamma_L( \hat{x}_0 ; N_x)$.
		    \For {$m = -\ell,\dots,\ell$}
		    \State Compute $W(k,s,i,j,\hat{x}_0)$ for $s = \bar{s} m / \ell$ using \eqref{eq:pgm}.
		    \EndFor  
		    \State Construct a $\mathcal{O}( \Delta x + \bar{s}/\ell + \varepsilon_{\rm tol})$ approximation of $\Pr(\check{x}_t, \hat{x}_0, \hat{v}_0)$ at $t=\ell \Delta t$ via Theorem \ref{thm:main} 
		    with partition $\mathcal{P}_\ell$ of \eqref{eq:partition}.
		   \label{alg1:step2}.
		    \State Normalize with respect to $\check{x}_t$ to obtain an approximation of $\Pr(\check{x}_t \mid \hat{x}_0, \hat{v}_0)$.
		    \State Convolve with respect to $\Pr( x_t \mid \check{x}_t)$ to obtain $\rho_t(x_t)$ at $t= \ell \cdot \Delta t$
		    \EndFor
		  \end{algorithmic}
\end{algorithm}
